Image restoration using dimensionality reduction in the Fourier domain

### 2011-06-06 project/Paper/paper.tex
Added rough draft of algorithm

\begin{document}
\title{Image restoration using dimension reduction in the Fourier domain}

@@

\section{Introduction}
In image inpainting, the aim is to restore an image from a disturbed source.
These distortions may, for example, result from a transmission over a noisy channel.
We distinguish inpainting from image 
((( TODO )))
The aim of writing a paper is to infect the mind of your reader with
the brilliance of your idea \cite{jones08}. 
The hope is that after reading your
paper, the audience will be convinced to try out your idea. In other
words, it is the medium to transport the idea from your head to your
reader's head.

\section{Methods}
\subsection{Related work}
((( TODO )))
\subsection{New approach}
((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.

>>>>

\begin{document}
\title{Image restoration using dimensionality reduction in the Fourier domain}

@@

\section{Introduction}
In image inpainting, the aim is to restore an image from a disturbed source.
These disturbances may, for example, result from a transmission over a noisy channel or from a degraded physical copy of the original image. Another application is object removal where a part of the image to be removed and the hole to be filled using inpainting.\\
In our approach, we use an iterative scheme with dimensionality reduction in the Fourier domain. 
((( TODO )))\\

The aim of writing a paper is to infect the mind of your reader with
the brilliance of your idea \cite{jones08}. 
The hope is that after reading your
paper, the audience will be convinced to try out your idea. In other
words, it is the medium to transport the idea from your head to your
reader's head.

\section{Methods}
\subsection{Related work}
((( TODO )))

\subsection{New approach}
(((REWRITE)))
We combine several ideas in our approach to obtain a inpainting algorithm that provides good results and fast performance.
Our algorithm requires as input the image which shall be restored and a mask which indicates the pixels that shall be filled. Such a mask can be created by the user or automatically (((? checksum))).\\
The main inspiration behind our algorithm is that we try to interpolate the pixels from its neighboring values. By this we add some noise compared to the original, undamaged image. We then try to use dimensionality reduction to filter out this generated noise to reconstruct the image.\\

We use an iterative scheme to determine the right parameters used in our algorithm. For this, we use cross-validation: We randomly remove a percentage of pixels from the image as a test set. We then use this test set to test the accuracy of our parameters and determine the best set of parameters for this image.

We then proceed to the main steps of the algorithm:
\begin{enumerate}
\label{algo}
\item \label{algo:step1}
We use a Gaussian to interpolate the missing pixels indicated by the mask, using a convolution operation. Both $\sigma$ and the size of the Gaussian matrix are determined by the cross-validation.
This step is required by the Fourier transform which cannot ignore samples. (((Humm)))

\item \label{algo:step2}
We transform the image to the Fourier domain. In this domain we set the magnitudes of all frequencies to zero which are below the $n$-th percentile threshold. Again, $n$ is determined by cross-validation.
(((EXPERIMENTAL: Validate, Rewrite))) We then repeat this step a certain number of times...

\item \label{algo:step3}
In this last step, we invert the Fourier transform and combine the reconstructed image with the undamaged part of the image, yielding our result.

\end{enumerate}

((( TODO )))
Describe your idea and how it was implemented to solve
  the problem. Survey the related work, giving credit where credit is
  due.
